---
title: "Kerala Rainfall Forecast"
output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
    vertical_layout: scroll
    social: menu
    source_code: embed
---
Last compiled on : `r format(Sys.time(), '%d %B, %Y')`



```{r setup, include=FALSE}

library(tidyverse)
library(sf)
library(lubridate)
library(flexdashboard)
library(leaflet)

# load data

source("warn.R", local = knitr::knit_global())

map_in <- st_read("./data/kerala/kerala_lak.shp")

weather_a  <- read_csv("./data/weather_warn.csv")


# re-code

weather_a[weather_a == "No rain"] <- "No alert"
weather_a[weather_a == "L." ] <- "Green alert"
weather_a[weather_a == "L. to M" ] <- "Green alert"
weather_a[weather_a == "L to M" ] <- "Green alert"
weather_a[weather_a == "VL" ] <- "No alert"
weather_a[weather_a == "VL." ] <- "No alert"
weather_a[weather_a == "M" ] <- "Yellow alert"
weather_a[weather_a == "M." ] <- "Yellow alert"
weather_a[weather_a == "M. to H" ] <- "Yellow alert"
weather_a[weather_a == "M to H" ] <- "Yellow alert"
weather_a[weather_a == "H" ] <- "Orange alert"
weather_a[weather_a == "H." ] <- "Orange alert"
weather_a[weather_a == "VH" ] <- "Red alert"
weather_a[weather_a == "VH." ] <- "Red alert"
weather_a[weather_a == "XH" ] <- "Red alert - Extremely heavy rainfall"
weather_a[weather_a == "XH." ] <- "Red alert - Extremely heavy rainfall"


# col

colnames(weather_a)[1] <- "Name_1"

# shp + csv

map_latest <- merge(map_in,weather_a, by ="Name_1") %>% 
  filter(!grepl('Lakshadweep', Name_1))


# Col names

col2 <- sym(names(map_latest)[2])
col3 <- sym(names(map_latest)[3])
col4 <- sym(names(map_latest)[4])
col5 <- sym(names(map_latest)[5])
col6 <- sym(names(map_latest)[6])



col <- colnames(map_latest[2:6])

# Leaflet ideas-----

# maplatest copy

map_ker <- map_latest %>% 
  `colnames<-`(c("District","d1","d2","d3","d4","d5","geometry"))

# color factor

pal <- 
  colorFactor(palette = c('White', '#188f14', 'Yellow', 'Orange', 'Red', '#8B0000'), 
              levels = c("No alert","Green alert","Yellow alert","Orange alert",
                         "Red alert","Red alert - Extremely heavy rainfall"))



m <- leaflet(map_ker) %>% 
  addTiles()  %>% 
  
  # Day 1
  addPolygons(fillColor  = pal(map_ker$d1), fillOpacity = .5,
              popup = paste("Date: ",col2, "<br>",
                            "District: ",map_ker$District, "<br>",
                            "Rainfall alert: ", map_ker$d1, "<br>"), group = col[1]) %>% 
  
  # Day 2
  addPolygons(fillColor  = pal(map_ker$d2), fillOpacity = .5,
              popup = paste("Date: ",col3, "<br>",
                            "District: ",map_ker$d1, "<br>",
                            "Rainfall alert: ", map_ker$d2, "<br>") , group = col[2]) %>% 
  
  #Day 3
  addPolygons(fillColor  = pal(map_ker$d3), fillOpacity = .5,
              popup = paste("Date: ",col4, "<br>",
                            "District: ",map_ker$d1, "<br>",
                            "Rainfall alert: ", map_ker$d3, "<br>") , group = col[3]) %>% 
  # Day 4
  addPolygons(fillColor  = pal(map_ker$d4), fillOpacity = .5,
              popup = paste("Date: ",col5, "<br>",
                            "District: ",map_ker$d1, "<br>",
                            "Rainfall alert: ", map_ker$d4, "<br>") , group = col[4]) %>% 
  
  # Day 5
  
  addPolygons(fillColor  = pal(map_ker$d5), fillOpacity = .5,
              popup = paste("Date: ",col6, "<br>",
                            "District: ",map_ker$d1, "<br>",
                            "Rainfall alert: ", map_ker$d5, "<br>") , group = col[5]) %>% 
  
  setView(lng = 76.5711, lat = 10.5, zoom = 7) %>%
  
  #addLegend(position = "bottomright",pal = pal,
            #values = c("No alert","Green alert","Yellow alert","Orange alert",
                       #"Red alert","Red alert - Extremely heavy rainfall") ) %>% 
  
  addLayersControl(overlayGroups = col[1:5] ,
                   options = layersControlOptions(collapsed = T))%>% 
  
  # add inset map
  addMiniMap(
    tiles = providers$Esri.OceanBasemap,
    position = 'bottomleft', 
    width = 120, height = 120,
    toggleDisplay = FALSE)
```



Rainfall alert 
=====================================  

Column {.tabset}
-----------------------------------------------------------------------

### Rainfall Alert for the week - Weather Forecast for Kerala

```{r echo=FALSE }
# Rainfall Alert for the week - Weather Forecast for Kerala

m %>% 
  hideGroup(col[2:5])
```


Info
=====================================  


What does these alerts actually mean ?
 
+--------------+--------------------------------------+------------------------+ 
| Type         | Intensity of rainfall                | Warning colour code    |
+==============+======================================+========================+
| No alert     | Very Light Rainfall (0.1 to 2.4 mm)  | No warning (No action) |
+--------------+--------------------------------------+------------------------+
| Green alert  | Light rainfall (2.5-15.5 mm)         | No warning (No action) |
+--------------+--------------------------------------+------------------------+
| Yellow alert | Moderate (15.6-64.4 mm)              | Watch (Be updated)     |
+--------------+--------------------------------------+------------------------+
| Orange alert | Heavy Rainfall (64.5-115.5 mm)       | Alert (Be prepared)    |
+--------------+--------------------------------------+------------------------+
| Red alert    | Very Heavy Rainfall (115.6-204,4 mm) | Warning (Take action)  |
+--------------+--------------------------------------+------------------------+
| Red alert    | Extremely Heavy Rainfall (>204.4mm)  | Warning (Take action)  |  
+--------------+--------------------------------------+------------------------+



* Source: [IMD Trivandrum](https://mausam.imd.gov.in/thiruvananthapuram)

* All maps are generated automatically from the INDIAN METEOROLOGICAL DEPARTMENT bulletin.
