---
title: "Kerala Rainfall Forecast"
output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
    vertical_layout: scroll
    social: menu
    source_code: embed
---


Last compiled on : `r format(Sys.time(), '%d %B, %Y')`



```{r setup, include=FALSE}

library(tidyverse)
library(sf)
library(glue)
library(lubridate)
library(flexdashboard)
library(ggiraph)


# load data

source("warn.R", local = knitr::knit_global())

map_in <- st_read("./data/kerala/kerala_lak.shp")

weather_a  <- read_csv("./data/weather_warn.csv")


# re-code

weather_a[weather_a == "No rain"] <- "0"
weather_a[weather_a == "L." ] <- "1"
weather_a[weather_a == "L. to M" ] <- "1"
weather_a[weather_a == "L to M" ] <- "1"
weather_a[weather_a == "VL" ] <- "0"
weather_a[weather_a == "VL." ] <- "0"
weather_a[weather_a == "M" ] <- "2"
weather_a[weather_a == "M." ] <- "2"
weather_a[weather_a == "M. to H" ] <- "2"
weather_a[weather_a == "M to H" ] <- "2"
weather_a[weather_a == "H" ] <- "3"
weather_a[weather_a == "H." ] <- "3"
weather_a[weather_a == "VH" ] <- "4"
weather_a[weather_a == "VH." ] <- "4"
weather_a[weather_a == "XH" ] <- "5"
weather_a[weather_a == "XH." ] <- "5"


# col

colnames(weather_a)[1] <- "Name_1"

# shp + csv

map_latest <- merge(map_in,weather_a, by ="Name_1") %>% 
  filter(!grepl('Lakshadweep', Name_1))


# Col names

col2 <- sym(names(map_latest)[2])
col3 <- sym(names(map_latest)[3])
col4 <- sym(names(map_latest)[4])
col5 <- sym(names(map_latest)[5])
col6 <- sym(names(map_latest)[6])

# Plot
warn_plot <- function(col) {
  g1 <- ggplot(map_latest) +
    geom_sf(aes(fill = !!col)) +
    geom_sf_interactive(aes(fill = !!col,tooltip = Name_1))+
    scale_fill_manual(name = "Rainfall alerts",
      labels = c(
        "No alert",
        "Green alert",
        "Yellow alert",
        "Orange alert",
        "Red alert",
        "Extreme heavy rainfall"
      ),
      values = c('White', '#188f14', 'Yellow', 'Orange', 'Red', '#8B0000')
    ) +
    labs(title = "Kerala Rainfall Forecast \n (for next five days)",
         subtitle = glue("Date: {col}-{year(now())}"),
         caption = "Source: INDIAN METEOROLOGICAL DEPARTMENT \nCreated by: Open-oven") +
    theme_void()+
    theme(
       plot.title = element_text(size = rel(1.5),family = "serif"),
       legend.title = element_text(face = "bold"),
       plot.caption = element_text(hjust = 0, face = "italic",colour = '#281bde'))
  
  girafe( ggobj = g1)
}

```

Maps 
=====================================  

Column {.tabset}
-----------------------------------------------------------------------

### Day 1 

```{r fig.width=8, fig.height=12, fig.fullwidth=TRUE, echo=FALSE }
# Plot Day 1

warn_plot(col2)
```

### Day 2 

```{r fig.width=8, fig.height=12, fig.fullwidth=TRUE , echo=FALSE}
# Plot Day 2
warn_plot(col3)
```



### Day 3  

```{r fig.width=8, fig.height=12, fig.fullwidth=TRUE, echo=FALSE}
# Plot Day 3
warn_plot(col4)
```

### Day 4 

```{r fig.width=8, fig.height=12, fig.fullwidth=TRUE, echo=FALSE}

# Plot Day 4
warn_plot(col5)
```

### Day 5  

```{r fig.width=8, fig.height=12, fig.fullwidth=TRUE, echo=FALSE}

# Plot Day 5

warn_plot(col6)
```


Info
=====================================  

What does these alerts actually mean ?
 
+--------------+--------------------------------------+------------------------+ 
| Type         | Intensity of rainfall                | Warning colour code    |
+==============+======================================+========================+
| No alert     | Very Light Rainfall (0.1 to 2.4 mm)  | No warning (No action) |
+--------------+--------------------------------------+------------------------+
| Green alert  | Light rainfall (2.5-15.5 mm)         | No warning (No action) |
+--------------+--------------------------------------+------------------------+
| Yellow alert | Moderate (15.6-64.4 mm)              | Watch (Be updated)     |
+--------------+--------------------------------------+------------------------+
| Orange alert | Heavy Rainfall (64.5-115.5 mm)       | Alert (Be prepared)    |
+--------------+--------------------------------------+------------------------+
| Red alert    | Very Heavy Rainfall (115.6-204,4 mm) | Warning (Take action)  |
+--------------+--------------------------------------+------------------------+
| Red alert    | Extremely Heavy Rainfall (>204.4mm)  | Warning (Take action)  |  
+--------------+--------------------------------------+------------------------+



* Source: [IMD Trivandrum](https://mausam.imd.gov.in/thiruvananthapuram)

* All maps are generated automatically from the INDIAN METEOROLOGICAL DEPARTMENT bulletin.






